
---
name: Thadryan
surname: Sweeney, MS
position: "Medical Data Scientist, Doctoral Student"
phone: +978 696 6946
www: "thadryanjs.github.io"
email: "thadryan@protonmail.com"
twitter: ThadryanJS
github: thadryanjs
linkedin: "thadryan-sweeney-10b938a"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

I am a Medical Data Scientist currently pursuing a PhD in Quantitative Biomedical Sciences at Dartmouth College. I am interested in developing and applying biostatistical and machine learning methods to improve the efficiency of health systems with a special focus on opioid-related harms. 

# Research Positions

```{r}

tribble(
  ~Degree, ~Year, ~Institution, ~Where,
  "Graduate Research Assistant", "2022-present", "Dartmouth College", "Hanover, NH",
  "Research Technologist", "2020-2022", "Mass General/Harvard Medical School", "Boston, MA",
  "Bioinformatics & Data Science Contractor", "2018-2019", "bluebird bio", "Cambridge, MA"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Education

```{r}

tribble(
  ~Degree, ~Subject, ~Year, ~Institution, ~Where,
  "Doctor of Philosophy", "Quantitative Biomedical Sciences", "In progress", "Dartmouth College", "Hanover, NH",
  "Master of Science",  "Bioinformatics", "2019", "Northeastern University",        "Boston, MA",
  "Bachelor of Science","Human Biology",  "2013", "American International College", "Springfield, MA",
  "Associate of Arts",  "Liberal Studies","2011", "Greenfield Community College",   "Greenfield, MA"
) %>% 
  detailed_entries(Degree, Year, Subject, Institution, Where)
```

# Teaching & Teaching Assistantship

```{r}

tribble(
  ~Year, ~Class, ~ Where, ~Role,
  2023, "Intermediate Programming for Data Science", "Dartmouth College", "Teaching Assistant",
  2023, "Applied Epidemiological Methods", "Dartmouth College", "Teaching Assistant",
  2022, "Bioinformatics Methods I (spring)", "Northeastern University", "Instructor",
  2021, "Bioinformatics Methods I (fall)", "Northeastern University", "Instructor",
  2021, "Bioinformatics Methods I (spring)", "Northeastern University", "Instructor",
  2020, "Bioinformatics Methods I (fall)", "Northeastern University", "Instructor",
  2020, "Bioinformatics Methods I (spring)", "Northeastern University", "Instrucor",
  2019, "Bioinformatics Programming", "Northeastern University", "Teaching Assistant",
  2018, "Collecting, Storing, and Retrieving Data", "Northeastern University", "Teaching Assistant",
  2018, "Introduction to Data Mining and Machine Learning", "Northeastern University", "Teaching Assistant",
) %>% 
  detailed_entries(Class, Year, Where, Role)
```

# Published Software

```{r}
tribble(
  ~Year, ~Type, ~Desc, 
  2020, "An interactive Bayesian Ttool for SARS-CoV2-Antibody test interpretation", "Manuscript supplement, https://covid.omics.kitchen/",
  2020, "ContrApption: interactive visualization of RNA-Seq style datasets from a single function call", "(beta) https://github.com/omics-kitchen/ContrApption",
) %>% 
  brief_entries(glue::glue("{Type}"), Year, Desc)
```

# Publications

## Published

```{R}

tribble(
  ~Year, ~Desc, ~Note,
  "2023", "Plasma biomarkers for diagnosis of Alzheimer’s disease and prediction of cognitive decline in individuals with mild cognitive impairment", "Frontiers in Neurology",
  
  "2022", "Increased levels of the synaptic proteins PSD-95, SNAP-25, and neurogranin in the cerebrospinal fluid of patients with Alzheimer’s disease", "Alzheimer's Research & Therapy",

  "2022", "Elevation of Neuronal Injury Markers in Patients with Neurologic Sequelae after Hospitalization for SARS-CoV-2 Infection", "Iscience",
  
  "2022", "Distinct stress-dependent signatures of cellular and extracellular tRNA-derived small RNAs (tDRs)", "Advanced Science",
   
  "2022", "A novel tissue atlas and online tool for the interrogation of small RNA expression in human tissues and biofluids", "Frontiers in Cell and Developmental Biology, supplement: https://data.omics.kitchen/miRNAatlas/",
  
  "2021", "Evaluation of serological lateral flow assays for severe acute respiratory syndrome coronavirus-2",
  "BMC Infectious Diseases, supplement: https://covid.omics.kitchen/",
  
) %>%
  detailed_entries(Desc, glue::glue("{Year}"), Note)
```

<!-- ## Accepted -->

```{R}

# tribble(
#   ~Year, ~Desc, ~Note,
#   "2021", "A novel tissue atlas and online tool for the interrogation of small RNA expression in human tissues and biofluids", "https://www.frontiersin.org/articles/10.3389/fcell.2022.804164/abstract",
# ) %>%
#   detailed_entries(Desc, glue::glue("{Year}"), Note)
```

<!-- ## In Revision -->

```{R}

# tribble(
#   ~Year, ~Desc, ~Note,
#   "2022", "Elevation of Neuronal Injury Markers in Patients with Neurologic Sequelae after Hospitalization for SARS-CoV-2 Infection", ""
# ) %>%
#   detailed_entries(Desc, glue::glue("{Year}"), Note)
```

<!-- ## Submitted -->

```{R}

# tribble(
#   ~Year, ~Desc, ~Note,
#   "2022", "Plasma biomarkers for diagnosis of Alzheimer’s disease and prediction of cognitive decline in individuals with mild cognitive impairment", ""
# ) %>%
#   detailed_entries(Desc, glue::glue("{Year}"), Note)
```

## In preparation

```{R}

tribble(
  ~Year, ~Desc, ~Note,
  "TBD", "miRNAs in canine mitral value disorders", "",
  "TBD", "ContrApption: interactive visualization of RNA-Seq style datasets from a single function call","",
) %>%
  detailed_entries(Desc, glue::glue("{Year}"), Note)
```


# Volunteer Work & "Hacktivism"

```{R}

tribble(
  ~Year, ~Desc, ~Note,
  "2020-2022", "Volunteer at RagTag (https://ragtag.org/)",
  "Core developer on The National Survivor Financial Security Policy Map and Scorecard 
  (https://mapandscorecard.freefrom.org/), a tool for evaluating how different states in the US
  promote the financial wellness of Survivors of intimate partner violence",
  "2008-2014", "Volunteer Firefighter/EMT: Orange Fire-Rescue-EMS", ""
) %>%
  detailed_entries(Desc, glue::glue("{Year}"), Note)
```

# Media

```{r}

tribble(
  ~Year, ~Desc, ~Note,
  2020, "COVID-19 LFA Research", "https://www.wcvb.com/article/boston-researchers-assess-performance-of-covid-19-antibody-tests/33625088"
) %>% 
  brief_entries(Desc, Year, Note)
```

# Pre-academic work

## Antibody Technician - New England Peptide

                              (Now 'Vivitide') 
                            Sept. ‘15 - Sept. ’17

```{R}

tribble(
  ~Year, ~Desc,
    ".", "Ran day-to-day operations of antibody production lab as sole technician",
    ".", "Self-taught Python programming to automate bioinformatics tasks, saving weeks of effort and dozens of errors",
    ".", "Studied and practiced antigen design under an industry leader",
) %>%
  brief_entries(Desc, glue::glue("{Year}"))
```

##
## Chemical Operator, Vinegar Plant - Pilgrim Foods

                            Mar. ‘15 - Sept. ’15

```{R}

tribble(
  ~Year, ~Desc,
    ".", "Inoculated, monitored, and maintained live cultures of Acetobacter for fermentation of ethanol to acetic acid",
    ".", "Redefined instrument calibration procedure by observing logarithmic trends in data previously modeled as linear",
    ".", "Formulated batches of mash to alcohol, acidity, stock, and water specifications",
) %>%
  brief_entries(Desc, glue::glue("{Year}"))
```

##
## Asst. Manager, Peer Counselor - The Bridge of Central Mass

                        (Now 'Open Sky Community Services')
                            Nov. ‘13 – Mar. ’15

```{R}

tribble(
  ~Year, ~Desc,
    ".", "Counseled individuals aged 18-25 in their recovery from mental illness and trauma",
    ".", "Provided quality assurance for medication administration and financial tracking",
    ".", "Supervised nine employees during shifts and on call from home for crisis management",
) %>%
  brief_entries(Desc, glue::glue("{Year}"))
```

##
## Firefighter/EMT - Orange Fire Rescue EMS

                            Jun. ‘08 – Sept. ‘14

```{R}

tribble(
  ~Year, ~Desc,
    ".", "Engaged in fire/rescue activities, structural and wildland firefighting, search operations, and trauma management",
    ".", "Responded to medical     emergencies, performed CPR/Basic life support, and administered medication",
    ".", "Participated in search and rescue operations and trainings, including ice rescue training and boat operations",
) %>%
  brief_entries(Desc, glue::glue("{Year}"))
```


